Practical Machine Learning - Prediction Assignment Writeup
==========================================================

Machine Learning analysis of the Weight Lifting Exercise Dataset using a random forest model. The caret and randomForest libraries were used to construct this analysis.


```{r, results='hide', echo=FALSE}
library(Hmisc)
library(caret)
library(randomForest)
library(foreach)
library(doParallel)
set.seed(2048)
options(warn=-1)
```

Loaded Data and added NA values where #DIV/0! values exsisted as a best practice.

```{r, results='hide'}
trainingUrl <- "http://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
testUrl <- "http://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"
training_data <- read.csv(trainingUrl, na.strings=c("#DIV/0!") )
test_data <- read.csv(testUrl, na.strings=c("#DIV/0!") )
```

Converted all columns to class numeric.

```{r}
for(i in c(8:ncol(training_data)-1)) {training_data[,i] = as.numeric(as.character(training_data[,i]))}

for(i in c(8:ncol(test_data)-1)) {test_data[,i] = as.numeric(as.character(test_data[,i]))}
```

Cleaned data chose a feature set that only included complete columns.  

Determine and display feature set.

```{r}
feature_set <- colnames(training_data[colSums(is.na(training_data)) == 0])[-(1:7)]
model_data <- training_data[feature_set]
feature_set
```

Create traing and test data sets and model.

```{r}
idx <- createDataPartition(y=model_data$classe, p=0.75, list=FALSE )
training <- model_data[idx,]
testing <- model_data[-idx,]
```

Built 5 random forests with 150 trees per forest.

```{r}
registerDoParallel()
x <- training[-ncol(training)]
y <- training$classe

rf <- foreach(ntree=rep(150, 6), .combine=randomForest::combine, .packages='randomForest') %dopar% {
randomForest(x, y, ntree=ntree) 
}
```

Error summarys for training and test data.

```{r}
predictions1 <- predict(rf, newdata=training)
confusionMatrix(predictions1,training$classe)


predictions2 <- predict(rf, newdata=testing)
confusionMatrix(predictions2,testing$classe)
```

Conclusion:
--------------------------------

The confusion matrix shows the model proved to be accurate when applied to the test set data, validating the modle choice.

